### 2018-08-08 paper/intro.tex
pass on intro

In this paper, we demonstrate how good performance can be reconciled
with strong privacy protection in file transfer systems. We present
\name{}, a novel fully decentralized, autonomous,
% approach that provides a 
and self-organizing file transfer service between the \squad{}s of different users that preserves user privacy
in terms of both data \emph{and} metadata. \commentFT{Moving to 3 ideas, to highlight proxemics in its own right} Our proposal hinges on three
key ideas: \emph{Firstly}, the emergence of \emph{\squad{}s}, the set of connected devices owned and used by one user, 
%% the recent advances of smartphones and other
%% mobile devices enable e-squads and it has thus
%% become possible to
makes it possible to apply P2P technology to one's own devices
alone, thereby reducing one's exposure to security and privacy threats
from third parties. \emph{Secondly}, we consider \emph{proxemics relationships} as a key enabler to initiate file
transfers. Physical proximity allow users to share
routing information out-of-band.
%, e.g. from their \squad. \commentFT{I did not get what 'from their \squad' mean.} 
In contrast to state-of-the-art P2P systems, users of \name agree out-of-band to share a file, but
do not keep it available for anyone else in the future. \emph{Thirdly}, we
exploit distributed machine learning techniques to predict the future
availability of user devices, and use this ability to implement a
\emph{probabilistic predictive onion routing} mechanism. The
predictive nature of our routing, exploited in a stateless way, allows
us to overcome the inherent fragility of pure P2P file transfer schemes.

@@

  \item We provide the Sphinxes mix-header format which extends 
    Sphinx~\cite{Sphinx} to a source-routed limited random-walk protocol --- 
    \ie each layer of the onion route contains several alternative next nodes.

  \item We provide the \ac{SPOR} node selection strategy for routing which, given a secure 
    \ac{RPS} protocol and availability estimates, selects nodes to populate the 
    layers of Sphinxes to maximize the availability of the route --- this 
    yields reliable routes even with low-availability nodes.

  \item We provide a protocol for a device squad to estimate the availabilities 
    of its own devices, based on Markov models and \squad overlays.
    These availabilities can then be used with \ac{SPOR}.
   % \commentDaniel{We should add some more details, maybe.}

  \item We use \ac{SPOR} to design \name \sonja{removed for
      redundancy, rephrased: a novel, fully decentralized, 
    autonomous and self-organizing} as a privacy-preserving file transfer service among
  users without third-party storage.

@@

In the following, in Section~\ref{system-model}, we state the
system and adversary models as well as the desired security and privacy properties of \name. Section~\ref{design}
introduces the design of our proposed solution. In
Sections~\ref{security-discussion} and \ref{Performance},
respectively, we evaluate the security and performance of our
approach. We set \name into context with related work in
Section~\ref{RelatedWork} and conclude with Section~\ref{conclusion}.

>>>>

In this paper, we demonstrate how good performance can be reconciled
with strong privacy protection in file transfer systems. We present
\name{}, a novel fully decentralized, autonomous,
% approach that provides a 
and self-organizing file transfer service between the \squad{}s of different users that preserves user privacy
in terms of both data \emph{and} metadata. \commentFT{Moving to 3 ideas, to highlight proxemics in its own right} Our proposal hinges on three
key ideas: \emph{Firstly}, the emergence of \emph{\squad{}s}, the set of connected devices owned and used by one user, 
%% the recent advances of smartphones and other
%% mobile devices enable e-squads and it has thus
%% become possible to
makes it possible to apply P2P technology to one's own devices
alone, thereby reducing one's exposure to security and privacy threats
from third parties. \emph{Secondly}, we consider \emph{proxemics relationships} as a key enabler to initiate file
transfers. Physical proximity allow users to share
routing information out-of-band.
%, e.g. from their \squad. \commentFT{I did not get what 'from their \squad' mean.} 
In contrast to state-of-the-art P2P systems, users of \name agree out-of-band to share a file, but
do not keep it available for anyone else in the future. \emph{Thirdly}, we
exploit distributed machine learning techniques to predict the future
availability of user devices, and use this ability to implement a
\emph{probabilistic predictive onion routing} protocol. Our protocol exploits a new mix-header format that uses onion layers made of sets of nodes rather single nodes. The use of multiple nodes in individual layers, together with our estimation of future device availability, exploited in a stateless way, allows
us to overcome the inherent fragility of pure P2P file transfer schemes while providing strong privacy properties.

@@

  \item We propose \Sphinxes, an extension of the
    Sphinx~\cite{Sphinx} mix-header format to set-based onion routing. \Sphinxes allows each layer of an onion route to contain several alternative next nodes, thus realizing a source-routed limited random-walk protocol.

  \item Building on \Sphinxes, we introduce the \ac{SPOR} %% node selection strategy for routing
    protocol
    that, given a secure 
    \ac{RPS} protocol and availability estimates, selects nodes to populate the 
    layers of \Sphinxes in order to maximize the availability of the route. This node selection procedure 
    yields reliable routes even in the presence of low-availability nodes while retaining the strong privacy properties of onion routing.

  \item We provide a protocol for a device \squad to estimate the availabilities 
    of its own devices, based on Markov models and \squad overlays.
    These estimated availabilities can then be exploited by \ac{SPOR} to populate \Sphinxes.
   % \commentDaniel{We should add some more details, maybe.}

  \item We use \ac{SPOR} to realize \name, \sonja{removed for
      redundancy, rephrased: a novel, fully decentralized, 
    autonomous and self-organizing} a privacy-preserving file transfer service among
  users that eschews any third-party storage or centralized bootstrapping service.

@@

The remainder of this paper is organized as follows. Section~\ref{system-model} presents the
system and adversary models as well as the desired security and privacy properties of \name. Section~\ref{design}
introduces the design of our proposed solution. In
Sections~\ref{security-discussion} and \ref{Performance},
respectively, we evaluate the security and performance of our
approach. We set \name into context with related work in
Section~\ref{RelatedWork} and conclude with Section~\ref{conclusion}.
